\section{Experiences}

\cventry{Dec 2024--May 2026}{Technical Support Specialist}{GanjeHost}{Tehran, Iran}{}{
    \begin{itemize}
%        \item Managed and optimized \textbf{vSphere clusters, ESXi servers}, and \textbf{HA pfSense nodes} for reliable traffic management.
%        \item Automated shared hosting deployments using \textbf{Bash} and \textbf{Ansible}, reducing setup time and improving efficiency.
%        \item Implemented monitoring with \textbf{Prometheus}, \textbf{Grafana}, and \textbf{Zabbix} for proactive issue detection.
%        \item Maintained \textbf{KVM clusters}, improving resource utilization and system performance.
%        \item Designed and deployed \textbf{network infrastructure} and data center layouts, managing MikroTik and Cisco equipment for a redundant, high-availability network.
%        \item Maintained \textbf{HPE server hardware and software}, ensuring stable and reliable operations.
         \item Provided advanced technical support via \textbf{tickets (WHMCS)} and \textbf{live troubleshooting} for Linux, networking, and hosting issues.
         \item Administered and optimized \textbf{cPanel} and \textbf{DirectAdmin}, managing shared hosting, migrations, backups, and performance.
         \item Deployed and maintained \textbf{Linux servers (LPIC-2)}, including process management, security, storage, and networking.
         \item Configured and troubleshot \textbf{DNS}, \textbf{LiteSpeed}, \textbf{Nginx}, and \textbf{mail servers} for high availability.
         \item Implemented and debugged \textbf{DKIM}, \textbf{SPF}, and \textbf{DMARC}, improving email deliverability and reputation.
         \item Maintained containerized services with \textbf{Docker}.
         \item Automated routine tasks using \textbf{Bash scripts}, reducing manual intervention and overhead.
         \item Optimized \textbf{WordPress} sites by analyzing resources, resolving plugin conflicts, and tuning performance.
         \item Monitored infrastructure with \textbf{Zabbix}, for proactive detection.
         \item Managed \textbf{KVM}, \textbf{vSphere} virtualization, ensuring efficient resource allocation and stable VPS operation.
         \item Maintained \textbf{HPE ProLiant servers} and RAID controllers, ensuring stable data center operations.
    \end{itemize}
}
